---
name: Matthew Hoctor, PharmD
position: "Public Health Pharmacist"
address: "Portland, OR"
email: "matthew.hoctor@mail.mcgill.ca"
phone: 518.708.9638
github: matthew-hoctor
linkedin: matthew-hoctor
date: "`r format(Sys.time(), '%B %Y')`"
# docname: "Curriculum Vitae - Matthew Hoctor"
# headcolor: #8000ff
# orcid: 0000-0001-7059-1940
output: 
  vitae::awesomecv:
    latex_engine: "xelatex"
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(readODS)
```

# Education

```{r}
read_ods("data.ods",
         sheet = "edu") %>%
  detailed_entries(
                 what = degree,
                 when = dates,
                 with = uni,
                 where = loc,
                 why = details)
```

# Licensure

```{r}
read_ods("data.ods",
         sheet = "lic") %>%
  detailed_entries(
                 what = license,
                 when = dates,
                 with = with,
                 where = where,
                 why = details)
```

# Selected Certifications

```{r}
read_ods("data.ods",
         sheet = "cert") %>%
  filter(include == 1) %>%
  detailed_entries(
    what = cert,
    # with = with,
    # where = where,
    when = when,
    why = why,
    )
```

# Experience

```{r}
read_ods("data.ods",
         sheet = "exp") %>%
  detailed_entries(
                 what = what,
                 when = when,
                 with = with,
                 # where = where,
                 where = place,
                 why = why)
```

\pagebreak

# Pharmacy Practice Experience

```{r}
read_ods("data.ods",
         sheet = "ppe") %>%
  detailed_entries(
                 what = what,
                 when = when,
                 with = with,
                 # where = where,
                 where = place,
                 why = why)
```

\pagebreak

# Volunteer Experience

```{r}
read_ods("data.ods",
         sheet = "vol") %>%
  detailed_entries(
                 what = what,
                 when = when,
                 with = with,
                 # where = where,
                 where = place,
                 why = why)
```


# Professional Organizations

```{r}
read_ods("data.ods",
         sheet = "prof") %>%
  detailed_entries(
                 what = what,
                 when = when,
                 with = with,
                 where = where,
                 why = why)
```

# Honors

```{r}
read_ods("data.ods",
         sheet = "hon") %>%
  detailed_entries(
                 what = what,
                 when = when,
                 with = with,
                 where = where,
                 why = why)
```

\pagebreak

# Selected Presentations

 * *Candida auris - A Proposal to Reduce Transmission & Selection of Resistant Strains*, Class Presentation, Current Issues in Public Health, **OHSU-PSU School of Public Health**, Mar 2022
 * *Long-Term Effects of Budesonide or Nedocromil in Children with Asthma*, Class Presentation, Applied Longitudinal Data Analysis, **OHSU-PSU School of Public Health**, Dec 2021
 * *Reducing Harms of Smoking in People Living With HIV*, Class Presentation, HIV/AIDS Epidemiology, **OHSU-PSU School of Public Health**, Dec 2021
 * *Cannabis Use and High Blood Pressure*, Class Presentation, Epidemiologic Data Analysis & Interpretation, **OHSU-PSU School of Public Health**, Aug 2021
 * *Atypical Antipsychotics*, Inservice Presentation, Pharmacy & Therapeutics Committee, **Ketchikan Indian Community Tribal Health Clinic**, Mar 2016
 * *Patient Case: Febrile Neutropenia*, Inservice Presentation, Clinical Pharmacy Staff Meeting, **Cancer Treatment Centers of America**, Jan 2016
 * *The Role of Theophylline in COPD Maintenance Therapy*, Inservice Presentation, **Temple University Hospital - Respiratory Intensive Care Unit**, Nov 2015
 * *Cisplatin Overdose Root Cause Analysis*, Class Presentation, Medication Error Surveillance and Control Planning, **Temple University School of Pharmacy**, Apr 2015
 * *Case Report: Brazil Nut Induced Type 1 Anaphylaxis*, Class Presentation, Adverse Drug Reactions II: Case Studies, **Temple University School of Pharmacy**, Apr 2015
 * *Accumulating Advantage*, Class Presentation, Outcomes of Diversity in the Pharmacy Practice, **Temple University School of Pharmacy**, Nov 2014
 * *Potential Public Health Benefits of Pharmacist Immunization in Pennsylvania*, Poster Presentation to Lawmakers and Public, **Pennsylvania Pharmacists Association**, Apr 2013
 * *Folate in Biochemical & Synthetic Catalytic Systems*, Class Presentation, Heterocyclic Organic Chemistry, **University at Albany**, Dec 2010
 * *Dichloro Methane - Reducing Lifecycle Impacts*, Class Presentation, Green Chemistry, **McGill University**, Mar 2008
 * *Process Development of 3-aminonapth-1-ol*, Poster Presentation **Albany Molecular Research International**, Aug 2007

```{r}
# read_ods("data.ods", 
#          sheet = "pres") %>%
#   detailed_entries(
#                  what = what,
#                  when = when,
#                  with = with,
#                  where = where,
#                  why = why)
```